// TODO: Add a listener for click events on the save button.
  // This code should use the id in the containing time-block as a key to save the user input in local storage.

  // HINT: What does `this` reference in the click listener function? (It selects the current HTML element)
  // How can DOM traversal be used to get the "hour-x" id of the time-block containing the button that was clicked?


  // How might the id be useful when saving the description in local storage?// (It will help us know what hour it is saved into)

  // TODO: Add code to apply the past, present, or future class to each time block by comparing the id to the current hour. 
  
  HINTS: How can the id attribute of each time-block be used to conditionally add or remove the past, present, and future classes? 
  (if the current time is true, then be red; if the current time is false, be green if +1 hour, be gray if -1 hour)
  How can Day.js be used to get the current hour in 24-hour time?
  //


  // TODO: Add code to get any user input that was saved in localStorage and set
  // the values of the corresponding textarea elements. HINT: How can the id
  // attribute of each time-block be used to do this?
  //





Done: 

// Wrap all code that interacts with the DOM in a call to jQuery to ensure that
// the code isn't run until the browser has finished rendering all the elements
// in the html. [X]

//Add code to display the current date in the header of the page. [X]

 

Original Code for timeblocks from tutoring

$(function () {
    var $timeBlocks = $('.time-block')
    
    $timeBlocks.each(function(){
      var blockHour = $(this).attr("id").split("-")[1];
      var dayjs = dayjs().format("H");
      console.log(hour)
      if (blockHour < dayjs){
        $(this).addClass("past")
      }
    })